microscopy Data Clean

### 2020-07-15 Microscopy Data Clean.Rmd
added some ideas about the butterfly plot

---
title: "microscopy Data Clean"
author: "Juan P Barraza"
date: "7/8/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(tidyr)
library(purrr)

@@

ggplot()+#plotting the absolute difference between strains only
  geom_jitter(data = tidysaRedSubtractResults1 %>% filter(Comparison=="mutantRatio") %>% filter(!Difference == 1),
              aes(x=TimePoint,y=Difference, color = Comparison, shape = Sample),size=3, height = 0, width = .2)+
  labs(title ="Variance comparison mutant/wt")+
  scale_y_log10(breaks = c(0.5,.25,1,2.5,5,10))+#breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```
#Functions for histograms
```{r new threshold images aggregates functions and data collection}
ReadAggregateFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = TRUE)
  colnames(datos)<-c('Size', 'Species')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}

@@

#now make them all factors
allAggregatesClean$Strain<-as.factor(allAggregatesClean$Strain)
allAggregatesClean$Sample<-as.factor(allAggregatesClean$Sample)
allAggregatesClean$TimePoint<-as.factor(allAggregatesClean$TimePoint)
allAggregatesClean$Position<-as.factor(allAggregatesClean$Position)
allAggregatesClean<-allAggregatesClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))

@@

#also for the redsubtract
allAggregatesredSubtractClean$Strain<-as.factor(allAggregatesredSubtractClean$Strain)
allAggregatesredSubtractClean$Sample<-as.factor(allAggregatesredSubtractClean$Sample)
allAggregatesredSubtractClean$TimePoint<-as.factor(allAggregatesredSubtractClean$TimePoint)
allAggregatesredSubtractClean$Position<-as.factor(allAggregatesredSubtractClean$Position)
allAggregatesredSubtractClean<-allAggregatesredSubtractClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
```

```{r new threshold agggregates, include=FALSE}
#get some stats on aggregates
allAggregateDataSummary<-allAggregatesClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))

allAggregateDataSummaryTime5wt<- allAggregateDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")

allAggregateredsubtractDataSummary<-allAggregatesredSubtractClean %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), sDAggSize = sd(Size), maxSize = max(Size), minSize = min(Size))

allAggregateredsubtractDataSummary0wt<- allAggregateredsubtractDataSummary %>% filter (TimePoint == 0) %>% filter(Strain=="PA14wt")%>% filter(Condition == "Pa:Sa 1:1") %>% filter(Species == "Pa")

#now I have to remove the one condition and add it from the removed
removeNonRedSubtractData<- allAggregateDataSummary %>% filter(!Condition == "Pa:Sa 1:1")
removeNonRedSubtractData$Position<-as.factor(removeNonRedSubtractData$Position)
removeNonRedSubtractData$Strain<-as.factor(removeNonRedSubtractData$Strain)
removeNonRedSubtractData$Sample<-as.factor(removeNonRedSubtractData$Sample)
removeNonRedSubtractData$TimePoint<-as.factor(removeNonRedSubtractData$TimePoint)

combinedRedSubtractData<-bind_rows(removeNonRedSubtractData,allAggregateredsubtractDataSummary)

@@

ggplot()+
  geom_jitter(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, shape = Strain), width = 0, height = 0)+
  geom_smooth(data = combinedRedSubtractData, aes(x = TimePoint, y= Aggs, color = Species, linetype = Strain, group = interaction(Species, Strain)))+
  facet_wrap(.~Condition)+
  scale_y_continuous(limits= c(0,1e4))+
  ggtitle('Number of aggregates per experiment')+
  labs(x = "Time (hours)",y = "Number of Aggregates")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#it turns out that there is little to no difference between the redsbutract images and the other ones =(
#now we filter for only the time point that we care, which is hour 5:
aggregatesDataTime5wt<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14wt")
aggregatesDataTime5mut<- combinedRedSubtractData %>% filter (TimePoint == 5) %>% filter(Strain=="PA14mut")

#this is a decent outline of the aggregates
ggplot()+
  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= meanAggSize, color = Species,shape = "MeanSize"), height = 0)+
  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= maxSize, color = Species, shape = "MaxSize"), height = 0)+
  geom_jitter(data = aggregatesDataTime5wt, aes(x = Condition, y= biomass, color = Species, shape = "TotalBiomass"), height = 0)+  
  #geom_smooth(data = aggregatesDataTime5, aes(x = , y= meanAggSize, color = Species, linetype = Strain, group = interaction(Species)))+
  facet_wrap(Species~.)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ggtitle('Aggregates summary: Mean, largest and total biomass')+
  labs(x = "Time (hours)",y = "um3")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

@@

```{r new threshold images histogram plots}
allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
allDataHistograms.10df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv',header=T)
allDataHistograms.50df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv',header=T)
allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)
allDataHistograms.100df<-allDataHistograms.100df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))
allDataHistograms.5df<-allDataHistograms.5df %>% mutate(Coculture = recode(Condition, "Sa Mono" = "No", "Pa Mono" = "No", "Pa:Sa 1:1" = "Yes","Pa:Sa 10:1"= "Yes", "Pa:Sa 1:100" = "Yes", "Pa:Sa 1:10" = "Yes"))

plotHist3DBiomassCountsLog<-function(df1, title){
  ggplot()+
    geom_point(data=df1,aes(x=max, y=frequency, color = Coculture, shape = Condition))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    xlab('Biomass (um^3)')+
    ylab('Frequency')+
    ggtitle(paste0(title," Raw biomass Distribution (bin size = 100 um)"))+
    facet_wrap(~TimePoint, nrow=4)
}
#This shows that the Sa biomass that gets eaten by Staph is from the largest aggregates, not from the small ones
plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Pa"), "Pa co-culture vs mono")

>>>>

---
title: "microscopy Data Clean"
author: "Juan P Barraza"
date: "7/8/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(dplyr)
library(gdata)
library(ggplot2)
library(cowplot)
library(magrittr)
library(tidyr)
library(purrr)
library(plotrix)#this is for std.error function
library(scales)#for negative log

@@

ggplot()+#plotting the absolute difference between strains only
  geom_jitter(data = tidysaRedSubtractResults1 %>% filter(Comparison=="mutantRatio") %>% filter(!Difference == 1),
              aes(x=TimePoint,y=Difference, color = Comparison, shape = Sample),size=3, height = 0, width = .2)+
  labs(title ="Variance comparison mutant/wt")+
  scale_y_log10(breaks = c(0.5,.25,1,2.5,5,10))+#breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```
#Reading aggregate data
```{r new threshold images aggregates functions and data collection}
ReadAggregateFile<-function(file, position, timepoint){#This function outputs total number of pixels in the csv file from matlab
  datos <-read.csv(file, header = TRUE)
  colnames(datos)<-c('Size', 'Species')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}

@@

#now make them all factors
allAggregatesClean$Strain<-as.factor(allAggregatesClean$Strain)
allAggregatesClean$Species<-as.factor(allAggregatesClean$Species)
allAggregatesClean$Sample<-as.factor(allAggregatesClean$Sample)
allAggregatesClean$TimePoint<-as.factor(allAggregatesClean$TimePoint)
allAggregatesClean$Position<-as.factor(allAggregatesClean$Position)
allAggregatesClean<-allAggregatesClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))

@@

#also for the redsubtract
allAggregatesredSubtractClean$Strain<-as.factor(allAggregatesredSubtractClean$Strain)
allAggregatesredSubtractClean$Species<-as.factor(allAggregatesredSubtractClean$Species)
allAggregatesredSubtractClean$Sample<-as.factor(allAggregatesredSubtractClean$Sample)
allAggregatesredSubtractClean$TimePoint<-as.factor(allAggregatesredSubtractClean$TimePoint)
allAggregatesredSubtractClean$Position<-as.factor(allAggregatesredSubtractClean$Position)
allAggregatesredSubtractClean<-allAggregatesredSubtractClean %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" ))
```
At this point I have 2 dataframes with aggregate data: allAggregatesredSubtractClean and allAggregatesClean, so now I have to merge them properly.
```{r agggregates stats and plots, include=FALSE}
removeNonRedSubtractData<- allAggregatesClean %>% filter(!Condition == "Pa:Sa 1:1")#remove Pa:Sa 1:1 condition
combinedRedSubtractData<-bind_rows(removeNonRedSubtractData,allAggregatesredSubtractClean)

combinedRedSubtractData$Condition<-as.factor(combinedRedSubtractData$Condition)
combinedRedSubtractData$Species<-as.factor(combinedRedSubtractData$Species)
combinedRedSubtractData$Position<-as.factor(combinedRedSubtractData$Position)
#I have to do this because the data frames had different number of factors on those columns...

#get some stats on aggregates
allAggregateDataSummary<-combinedRedSubtractData %>% group_by(Species,Condition, TimePoint, Sample, Strain) %>% summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>% ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono","Pa:Sa 1:1" = "Co"))

@@

#now we filter for only the time point that we care, which is hour 5:
aggregatesDataTime5wt<- allAggregateDataSummary %>% filter (TimePoint == 5) %>% filter(Strain=="PA14wt")
aggregatesDataTime5mut<- allAggregateDataSummary %>% filter (TimePoint == 5) %>% filter(Strain=="PA14mut")

#this is a decent outline of the aggregates data
ggplot()+#for wt
  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize, color = Species,shape = "MeanSize"))+
  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= maxSize, color = Species, shape = "MaxSize"))+
  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= biomass, color = Species, shape = "TotalBiomass"))+  
  facet_wrap(Species~.)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ggtitle('Aggregates: Mean, largest and total biomass (wild type)')+
  labs(x = "",y = "Aggregate size (um3)")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

ggplot()+#for mutant
  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize, color = Species,shape = "MeanSize"))+
  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= maxSize, color = Species, shape = "MaxSize"))+
  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= biomass, color = Species, shape = "TotalBiomass"))+  
  facet_wrap(Species~.)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ggtitle('Aggregates: Mean, largest and total biomass (pqsL mutant)')+
  labs(x = "",y = "um3")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

#now do only average aggregate size:
#wild type
ggplot()+
  geom_point(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize, shape = Sample))+
  geom_errorbar(data = aggregatesDataTime5wt, aes(x = ConditionNew, ymin= meanAggSize-seAggSize,ymax= meanAggSize+seAggSize))+
  facet_grid(~Species, space = "free")+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ggtitle('Mean Aggregate size per sample (wt)')+
  labs(x = "",y = "Aggregate size (um3)")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#mutant
ggplot()+
  geom_point(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize, shape = Sample))+
  geom_errorbar(data = aggregatesDataTime5mut, aes(x = ConditionNew, ymin= meanAggSize-seAggSize,ymax= meanAggSize+seAggSize))+
  facet_grid(~Species, space = "free")+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  ggtitle('Mean Aggregate size per sample (pqsL)')+
  labs(x = "",y = "um3")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

#very interesting...now do stats

aggregatesDataTime5mutStats<-aggregatesDataTime5mut %>% group_by (Species,ConditionNew, Strain) %>% 
  summarise(MeanAggs = mean(Aggs), SEAggs = std.error(Aggs), 
            MeanBiomass = mean(biomass),SEBiomass = std.error(biomass), 
            MeanAggSize = mean(meanAggSize), SEAggSize = std.error(meanAggSize))

aggregatesDataTime5wtStats<-aggregatesDataTime5wt %>% group_by (Species,ConditionNew, Strain) %>% 
  summarise(MeanAggs = mean(Aggs), SEAggs = std.error(Aggs), 
            MeanBiomass = mean(biomass),SEBiomass = std.error(biomass), 
            MeanAggSize = mean(meanAggSize), SEAggSize = std.error(meanAggSize))
```

```{r aggregate mean volume final figures}
#final figures potentially for paper
ggplot()+
  geom_jitter(data = aggregatesDataTime5wt, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
  geom_point(data = aggregatesDataTime5wtStats, aes(x = ConditionNew, y= MeanAggSize), size = 3, shape = 16)+
  geom_errorbar(data = aggregatesDataTime5wtStats, aes(x = ConditionNew, ymin= MeanAggSize-SEAggSize,ymax= MeanAggSize+SEAggSize), width = .5)+
  facet_grid(~Species, space = "free")+
  scale_y_log10( limits = c(1e0,1e2))+
  ggtitle('Aggregate size (wild type)')+
  labs(x = "",y = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

ggplot()+
  geom_jitter(data = aggregatesDataTime5mut, aes(x = ConditionNew, y= meanAggSize), size = 1, height = 0, width = .3, shape = 1)+
  geom_point(data = aggregatesDataTime5mutStats, aes(x = ConditionNew, y= MeanAggSize), size = 3, shape = 16)+
  geom_errorbar(data = aggregatesDataTime5mutStats, aes(x = ConditionNew, ymin= MeanAggSize-SEAggSize,ymax= MeanAggSize+SEAggSize), width = .5)+
  facet_grid(~Species, space = "free")+
  #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1e0,1e2))+
  scale_y_log10( limits = c(1e0,1e2))+
  ggtitle('Aggregate size (pqsL mutant)')+
  labs(x = "",y = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r aggregates extra metrics calculated}

@@

```{r histogram plots data}
allDataHistograms.5df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms5.csv',header=T)
allDataHistograms.10df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms10.csv',header=T)
allDataHistograms.50df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms50.csv',header=T)
allDataHistograms.100df<-read.csv(file='/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Histograms1/histograms100.csv',header=T)

hist.100<-allDataHistograms.100df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))
allDataHistograms.5df <- allDataHistograms.5df %>% filter(TimePoint== 5) %>% filter( Condition %in% c("Sa Mono", "Pa Mono", "Pa:Sa 1:1")) %>% mutate(ConditionNew = recode(Condition, "Sa Mono" = "Mono", "Pa Mono" = "Mono", "Pa:Sa 1:1" = "Co"))

#ok so I am going to try to do this...I can't do bar graphs because the width of the bars is too thin to be able to be seen by the viewer, so I am doing points
#I also want to do mono and co pointing to opposite sides, but I haven't been able to do it with recode, so I'll manually do it.
mono<- allDataHistograms.5df %>% filter(ConditionNew == "Mono") %>%  group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))
co<- allDataHistograms.5df %>% filter(ConditionNew == "Co") %>% group_by(max, Species, ConditionNew, Strain) %>% summarise(Frequency = sum(frequency))

#this is still showing the bins per sample, so I want to add the bins on each sample
ggplot()+
  geom_point(data = both %>% filter(Species == "Sa"), aes(y = max,x = CombinedFrequency, color = ConditionNew),stat = "identity", width = .6)+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
                              #coord_flip() +  # Flip axes
                              theme(plot.title = element_text(hjust = .5), 
                                    axis.ticks = element_blank()) +   # Centre plot title
                              theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))  # Color palette

ggplot()+
  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Mono"), 
                 aes(x = max, y= -1000-CombinedFrequency,color = ConditionNew), size = 2, alpha = 0.8)+
  geom_point(data = both %>% filter(Species == "Sa"& ConditionNew=="Co"), 
                 aes(x = max, y=1000+CombinedFrequency, color = ConditionNew), size = 2, alpha = 0.8)+
  #geom_label(aes(x = max, y = 0, label = max), 
#         inherit.aes = F,
#         size = 3.5, label.padding = unit(0.0, "lines"), label.size = 0,
#         label.r = unit(0.0, "lines"), fill = "#EFF2F4", alpha = 0.9, color = "#5D646F")+
  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #scale_y_continuous(breaks = c(c(-2, -1.5, -1, -0.5, 0) + -0.3, c(0, 0.5, 1, 1.5, 2)+0.3),
   #              labels = c("2", "1.5", "1", "0.5", "0", "0", "0.5", "1", "1.5", "2"))+
  facet_wrap(~Strain, ncol = 2)+
  coord_flip()+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))  # Color palette

#######
#testing negative exponential
reverselog_trans <- function(base = exp(1)) {
    trans <- function(x) -log(x, base)
    inv <- function(x) base^(-x)
    trans_new(paste0("reverselog-", format(base)), trans, inv, 
              log_breaks(base = base), 
              domain = c(1e-100, Inf))
}

monoPlot<-ggplot()+
  geom_point(data = mono %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
  scale_y_continuous(trans=reverselog_trans(base=10),
                     labels=trans_format("log10", scales::math_format(10^.x)))+
  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5), position = "top")+
  coord_flip()+
  xlab("")+
  ylab("Frequency")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

coPlot<-ggplot()+
  geom_point(data = co %>% filter(Species == "Sa"),aes(x = max, y= Frequency), size = 2, alpha = 0.8)+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = c(1e0,5e5))+
  coord_flip()+
  xlab("")+
  ylab("Frequency")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

########

plotHist3DBiomassCountsLog<-function(df1, title){
  ggplot()+
    geom_point(data=df1,aes(y=max, x=frequency, color = ConditionNew, shape = Strain))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    ylab('Biomass (um^3)')+
    xlab('Frequency')+
    #facet_wrap(~Sample, ncol=3)+
    ggtitle(paste0(title," Raw biomass Distribution (bin size = 100 um)"))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

#This shows that the Sa biomass that gets eaten by Staph is from the largest aggregates, not from the small ones
plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
plotHist3DBiomassCountsLog(allDataHistograms.100df %>% filter(Species == "Pa"), "Pa co-culture vs mono")
plotHist3DBiomassCountsLog(allDataHistograms.5df %>% filter(Species == "Sa"), "Sa co-culture vs mono")
